Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
move cast calc value typing

\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}

@@

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2}
	}
	\stxrulecont{
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3}
	}
	\stxrulecont{
		\eOOcast{e}{T_1}{l}{T_2} \mid
		\eOOblame{l}
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			\Gamma \vdash e : T_1 & T_1 \sim T_2
		}{
			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}

Let $ S,T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy
  \\---\\
  Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

@@

	\stxrule{v}{values}{
		\vOOfun{\rho}{x}{b} \mid
		\vOOtt{} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

@@

	Value typing \fbox{$ v : T $}
	\begin{gather*}
	\dots \quad
	\inference{
		v : P &
		c : P \Longrightarrow T &
		P \smile T
	}{
		\vOOcast{v}{\cOOcast{P}{l}{T}} : T
	}
	\end{gather*}

@@

	& \dots  \\
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
		\langle\cOOcast{T_3}{l}{T_1}\rangle
		(\mathtt{app_2} \; v_2 \; 
		\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}

@@

  Syntax
  \[
  \begin{array}{rclr}
     \stxrule{I}{injectable types}{
		\POOfun{\star}{\star} \mid \POOunit \mid \star \times \star \mid \star + \star}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

>>>>

\newcommand{\eOOcast}[2]{#1 \langle #2 \rangle}

@@

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2}
	}
	\stxrulecont{
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3}
	}
	\stxrulecont{
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOfun{\rho}{x}{e} \mid
		\vOOtt{} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			\Gamma \vdash e : T_1 & T_1 \sim T_2
		}{
			\judgetype{\Gamma}{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

	Value typing \fbox{$ v : T $}
	\begin{gather*}
	\dots \quad
	\inference{
		v : I
	}{
		\vOOcast{v}{\cOOcast{I}{l}{\TOOdyn}} : \TOOdyn
	}
	\quad
	\inference{
		v : P_1 &
		P_1 \smile P_2
	}{
		\vOOcast{v}{\cOOcast{P_1}{l}{P_2}} : P_2
	}
	\end{gather*}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
Let $ S,T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

@@

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

@@

@@

	& \dots  \\
	\redrule{
		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
		\langle\cOOcast{T_3}{l}{T_1}\rangle
		(\mathtt{app_2} \; v_2 \; 
		\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}

@@

  Syntax
  \[
  \begin{array}{rclr}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]
